---
title: ""
format: 
  gfm:
    keep_md: true
editor_options: 
  markdown: 
    wrap: sentence
---

# README 

```{r}
#| include: false
#| echo: false

library(tidyverse)
library(gert)
library(glue)
library(fs)
knitr::opts_chunk$set(echo = F, message = F, warning = F)

```
<br>

This repository contains data, code, and output for a manuscript entitled "Does computational modeling yield invariant measures of executive functioning?".

Do you want to download or clone the materials for this project? Go to [https://github.com/stefanvermeent/DDM_DIF](https://github.com/stefanvermeent/DDM_DIF). Please note that this is still a work in progress. As a result, some of the files and links mentioned below may not be available just yet.

## Directory Structure {#structure}

The directory structure follows the [TIER Protocol](https://www.projecttier.org/tier-protocol/protocol-4-0/).
The names of each folder are intended to be self-explanatory.
Each main folder contains its own README file to explain its content.

```{r}
#| echo: false
fs::dir_tree()
```

## Reproducing our results

### 1. Accessing LISS data

This GitHub repository does not contain raw or intermediate data files, as access to LISS data requires a signed data use agreement.
If you want to fully reproduce our analysis pipeline, you should first sign a [Data use agreement with LISS](https://liss.statements.centerdata.nl/). 
At the time of writing this README, accessing LISS data is free of charge.

Upon receiving access, you can download the data at <https::/lissdata.nl>. See [the Data Sources Guide](https://github.com/stefanvermeent/tree/main/1_InputData/DataSources.txt) for an overview of all the required files and their exact source.

*Note*: It is possible to **partially** reproduce our findings with the output files that are present on this repository. See step 2 below for more information.

### 2. Reproduce results

There are two ways to reproduce our results:

1.   **Full reproduction.** If you have followed the instructions under step 1, full reproduction (i.e., from preprocessing to building the manuscript file) is possible. The easiest way to achieve this is by running [2_scripts/MasterScript.R](https://github.com/StefanVermeent/tree/main/2_scripts/MasterScript.R), which executes all preprocessing and analysis scripts in the correct order. Please be aware that running the entire pipeline is very computationally costly---mostly due to DDM and MNLFA estimation. We strongly advice doing this in a high-performance cloud-computing environment that contains a large number of cores.

2.   **Partial reproduction.** Without access to the raw data, you can still render the manuscript and supplemental materials using the output files that are available on the public repository. 

## Contact

For questions or comments, please feel free to contact me at p.c.s.vermeent@gmail.com.
