---
bibliography: ../bibfiles/references.bib
csl: ../bibfiles/apa.csl
format: 
  docx:
    reference-doc: ../bibfiles/reference-doc-supp.docx
output:
  officedown::rdocx_document:
    plots:
      align: center
      caption:
        pre: 'Figure '
        sep: '. '
        style: Image Caption
    tables:
      caption:
        pre: 'Table '
        sep: '. '
        style: Table Caption
---

```{r}
#| warning: false
#| echo: false
library(tidyverse)
library(flextable)
load("../3_output/SupplementResults/section1.RData")
load("../3_output/SupplementResults/section2.RData")
```
# Supplementary materials

This file contains the supplementary materials for the article entitled "Unpacking differential item functioning in executive functioning performance using computational modeling".
The supplemental materials include supporting information relating to more detailed descriptive statistics, model convergence and fit, and details on confounders.

## Section 1 - Psychometric properties of cognitive tasks

### 1.1 Performance distributions

Figure S1 and S2 show the distributions of mean response times and mean error rate for each cognitive task.

```{r}
#| echo: false
#| warning: false
#| label: FigureS1
#| fig-width: 6
#| fig-height: 4.5
#| dpi: 600
#| fig-cap: | 
#|   **Figure S4.** Distributions of response times for all tasks.
supp_fig_rt_hist +
  theme_classic()
```

```{r}
#| echo: false
#| label: FigureS2
#| fig-width: 6
#| fig-height: 4.5
#| dpi: 600
#| fig-cap: | 
#|   **Figure S5.** Distributions of error rates for all tasks.
supp_fig_acc_hist +
  theme_classic()
```

### 1.2 Condition effects

Table S1 presents tests of condition effects for response times for the five cognitive tasks.
Specifically, we tested whether incongruent/switch trials led to significantly slower average correct responses relative to congruent/repeat trials.
The manipulation checks were based on mean log-transformed response times using paired-sample *t*-tests.
For each task, we tested whether there was a significant difference in mean log-transformed response time between the congruent (repeat) condition and the incongruent (switch) condition.
All tasks showed a significant difference in the expected direction, with participants on average being faster on the congruent (repeat) condition compared to the incongruent (switch) condition (all *p*s < .001).

```{r}
#| echo: false
#| tab.id: tableS1
#| results: markup
man_checks |> 
  flextable() |> 
  add_header_row(
    values = " ",
    colwidths = 4
  ) |> 
  flextable::compose(
    i = 1, j = 1,
    as_paragraph(as_b("Table S1. "), "Log-transformed response time differences across conditions for each task."),
    part = "header"
  ) |> 
  flextable::align(i = 2, align = "center", part = "header") |> 
  border_remove() |> 
  border(i = 2, border.top = fp_border_default(), part = "header") |>  
  border(i = 2, border.bottom = fp_border_default(), part = "header") |> 
  border(i = 5, border.bottom = fp_border_default(), part = "body") |> 
  autofit()
  
```


 


### 1.3 Split-half reliability

For each cognitive task, we calculated split-half reliabilities using the `splithalf` package [@parsons_2021].
We calculated split-half reliabilities for mean response times and error rates, separately for each condition (see Table S1).
The split-half reliability of mean response times was high across all tasks and conditions.
For error rates, the reliability estimates were generally lower, which is likely due to ceiling effects (see also Figure S5).

 

```{r}
#| echo: false
#| tab.id: tableS2
#| results: markup
sh_rel_rt_table |> 
  mutate(empty = "") |> 
  select(task, `sh_ci_congruent/repeat`, `sh_ci_incongruent/switch`, empty, `sb_ci_congruent/repeat`, `sb_ci_incongruent/switch`) |> 
  flextable() |> 
  flextable::set_header_labels(values = c("Task", "Congruent/Repeat", "Incongruent/Switch", "", "Congruent/Repeat", "Incongruent/Switch")) |> 
  add_header_row(values = c("", "Split-half reliability", "", "", "Spearman-Brown corrected", "")) |> 
  flextable::merge_at(i = 1, j = 2:3, part = "header") |> 
  flextable::merge_at(i = 1, j = 5:6, part = "header") |> 
  add_header_row(
    values = " ",
    colwidths = 6
  ) |> 
  flextable::compose(
    i = 1, j = 1,
    as_paragraph(as_b("Table S2. "), "Split-half reliabilities of mean response times for all cognitive tasks."),
    part = "header"
  ) |> 
  flextable::align(i = 2, align = "center", part = "header") |> 
  border_remove() |> 
  border(i = 2, border.top = fp_border_default(), part = "header") |>  
  border(i = 2, j = c(2:3, 5:6), border.bottom = fp_border_default(), part = "header") |> 
  border(i = 3, j = c(1:6), border.bottom = fp_border_default(), part = "header") |> 
  border(i = 5, border.bottom = fp_border_default(), part = "body") |> 
  autofit()
```

 {{< pagebreak >}}

```{r}
#| echo: false
#| tab.id: tableS3
#| results: markup
sh_rel_acc_table |> 
  mutate(empty = "") |> 
  select(task, `sh_ci_congruent/repeat`, `sh_ci_incongruent/switch`, empty, `sb_ci_congruent/repeat`, `sb_ci_incongruent/switch`) |> 
  flextable() |> 
  flextable::set_header_labels(values = c("Task", "Congruent/Repeat", "Incongruent/Switch", "", "Congruent/Repeat", "Incongruent/Switch")) |> 
  add_header_row(values = c("", "Split-half reliability", "", "", "Spearman-Brown corrected", "")) |> 
  flextable::merge_at(i = 1, j = 2:3, part = "header") |> 
  flextable::merge_at(i = 1, j = 5:6, part = "header") |> 
  add_header_row(
    values = " ",
    colwidths = 6
  ) |> 
  flextable::compose(
    i = 1, j = 1,
    as_paragraph(as_b("Table S3. "), "Split-half reliabilities of error rates for all cognitive tasks."),
    part = "header"
  ) |> 
  flextable::align(i = 2, align = "center", part = "header") |> 
  border_remove() |> 
  border(i = 2, border.top = fp_border_default(), part = "header") |>  
  border(i = 2, j = c(2:3, 5:6), border.bottom = fp_border_default(), part = "header") |> 
  border(i = 3, j = c(1:6), border.bottom = fp_border_default(), part = "header") |> 
  border(i = 5, border.bottom = fp_border_default(), part = "body") |> 
  autofit()
```

 

## Section 2 - DDM convergence and fit

### 2.1 Model convergence

Figures S3-S7 present the convergence of MCMC chains of the Hierarchical Drift Diffusion Models for all tasks.
The figures should resemble a "fat, hairy caterpillar", which was the case for all tasks.

 

 

```{r}
#| echo: false
#| label: FigureS3
#| fig-width: 6
#| fig-height: 3
#| dpi: 600
#| fig-cap: | 
#|   **Figure S3.** Trace convergence across three chains for the Flanker Task.
flanker_fit_trace
```

 

```{r}
#| echo: false
#| label: FigureS4
#| fig-width: 6
#| fig-height: 3
#| dpi: 600
#| fig-cap: | 
#|   **Figure S4.** Trace convergence across three chains for the Simon Task.
simon_fit_trace
```

 

```{r}
#| echo: false
#| label: FigureS5
#| fig-width: 6
#| fig-height: 3
#| dpi: 600
#| fig-cap: | 
#|   **Figure S5.** Trace convergence across three chains for the Color-shape Task.
colorshape_fit_trace
```

 

```{r}
#| echo: false
#| label: FigureS6
#| fig-width: 6
#| fig-height: 3
#| dpi: 600
#| fig-cap: | 
#|   **Figure S6.** Trace convergence across three chains for the Global-local Task.
globallocal_fit_trace
```

 

```{r}
#| echo: false
#| label: FigureS7
#| fig-width: 6
#| fig-height: 3
#| dpi: 600
#| fig-cap: | 
#|   **Figure S7.** Trace convergence across three chains for the Animacy-size Task.
animacysize_fit_trace
```
 

### 2.2 Model fit

Table S3 presents simulation-based model fit results.

{{< pagebreak >}}

:::{.landscape}

```{r}
#| echo: false
ddm_fit_table |> 
  flextable::autofit() |> 
  add_header_row(
    values = " ",
    colwidths = 7
  ) |> 
  flextable::compose(
    i = 1, j = 1,
    as_paragraph(as_b("Table S3. "), "Model fit assessment."),
    part = "header"
  ) |> 
  flextable::align(i = 2, align = "center", part = "header") |> 
  border_remove() |> 
  border(i = 2, border.top = fp_border_default(), part = "header") |>  
  border(i = 2, border.bottom = fp_border_default(), part = "header") |>  
  border(i = 10, border.bottom = fp_border_default(), part = "body") |> 
  add_footer_row(
    values = " ",
    colwidths = 7
  ) |> 
  add_footer_row(
    values = " ",
    colwidths = 7
  ) |> 
  flextable::compose(
    i = 1, j = 1, 
    as_paragraph(as_i("Note: "), "Simulation-based model fit assessment compared observed and predicted data using 100 simulated trials (accuracy, 25th, 50th, 75th percentile). In addition, we calculated R^ values, which should be below 1.1 to indicate adequate chain convergence."), 
    part = "footer"
  ) |> 
  flextable::autofit()
```

:::

# 3. References